Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-05 paper/preprint/appendix.Rmd
wrangling lmer tables

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
```

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range."}

@@

library(lmerTest)
library(sjPlot)
library(sjmisc)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes
```

@@

```{r}
face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(face_sit) # ns
tab_model(face_sit, show.re.var=F, dv.labels = "Proportion of Faces")
```

```{r}
hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(hand_sit) # ns
tab_model(hand_sit, show.re.var=F, dv.labels = "Proportion of Hands")
```

@@

```{r}
face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(face_cruise) 
# age+., cruise+*, age*cruise-*
tab_model(face_cruise, show.re.var=F, dv.labels = "Proportion of Faces")
```

@@

```{r}
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
summary(hand_cruise) 
# cruise+*, age*cruise-.
tab_model(hand_cruise, show.re.var=F, dv.labels = "Proportion of Hands") # show.obs=F
```

@@

```{r}
face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
#summary(face_walk) # ns
tab_model(face_walk, show.re.var=F, dv.labels = "Proportion of Faces")
```

```{r}
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
#summary(hand_walk) # walk+.
tab_model(hand_walk, show.re.var=F, dv.labels = "Proportion of Hands")
```

>>>>

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)

knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

@@

```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range.", warning=F}

@@

library(lmerTest)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes

face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
# make models compatible with stargazer
class(face_sit) <- "lmerMod"
class(hand_sit) <- "lmerMod"
class(face_cruise) <- "lmerMod"
class(hand_cruise) <- "lmerMod"
class(face_walk) <- "lmerMod"
class(hand_walk) <- "lmerMod"
```

@@

```{r, include=F, results='asis'}
#summary(face_sit) # ns
stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Faces")

stargazer(face_sit, hand_sit)
```

```{r, include=F, results='asis'}
#summary(hand_sit) # ns
stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

@@

```{r, include=F, results='asis'}
#summary(face_cruise) 
# age+., cruise+*, age*cruise-*
stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Faces")
```

@@

```{r, include=F, results='asis'}
#summary(hand_cruise) 
# cruise+*, age*cruise-.
stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Hands") 
```

```{r, results='asis'}
stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

@@

```{r, include=F, results='asis'}
#summary(face_walk) # ns
stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Faces")
```

```{r, include=F, results='asis'}
#summary(hand_walk) # walk+.
stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```
